Russo Fig1 Replots

### 2025-04-17 RussoPaper/20250314_RussoManuscript_Fig1Revisions.Rmd
updated general data files for app

B = B[c("w1118", "WTloxP", "G85Rhr", 
        "WTcr", "G85Rcr", "A4V.A4V",
        "null26.null26", "WTcr.null26",
        "G85Rcr.null26", "A4V.X16",
        "A4V.G85Rcr")]

@@

B.labels = c("w1118",
             "WTLoxP/WTLoxP", "G85R/G85R(HR)",
             "WT/WT(CR)", "G85R/G85R(CR)",
             "A4V/A4V", "Sod1null/Sod1null", 
             "WT/Sod1null", "G85R(CR)/Sod1null",
             "A4V/X16", "A4V/G85R(CR)")

@@

barplot(height = mean.B,
        ylim = c(0, 100),
        col = "black",
        las = 2,
        ylab = "Eclosion rate (%)",
        main = "Eclosion from the pupal case",
        xaxt = "n")
axis(side = 1,
     at = c(.7 + (c(0:10)*1.2)),
     lwd = 3,
     line = 0,
     labels = B.labels,
     xpd = T,
     las = 2)
axis(side = 2,
     at = c(0,20,40,60,80,100),
     lwd = 3,
     line = 0,
     labels = F,
     xpd = T)
lines(x = c(-0.5,13.5),
     y = c(0,0),
     lwd = 3,
     xpd = T)

>>>>

@@

B.labels = c("w1118",
             "WT(LoxP)", "G85R(hr)",
             "WT(cr)", "G85R(cr)",
             "G85R(cr)/Sod1null", "WT(cr)/Sod1null", "Sod1null", 
             "A4V/A4V", "A4V/Sod1null","A4V/X16", "A4V/G85R(cr)")

@@

barplot(height = mean.B,
        ylim = c(0, 100),
        col = "black",
        las = 2,
        ylab = "Eclosion frequency (%)",
        main = "Eclosion from the pupal case",
        xaxt = "n")
axis(side = 1,
     at = c(.7 + (c(0:11)*1.2)),
     lwd = 3,
     line = 0,
     labels = B.labels,
     xpd = T,
     las = 2)
axis(side = 2,
     at = c(0,20,40,60,80,100),
     lwd = 3,
     line = 0,
     labels = F,
     xpd = T)
lines(x = c(-0.5,13.5),
     y = c(0,0),
     lwd = 3,
     xpd = T)
